Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-06-25 docs/ms_sageAbundance.Rmd
updates ms to RMD rather than Rnw

\documentclass[12pt]{article}
\usepackage{graphics}
\usepackage{graphicx, verbatim}
\usepackage{amssymb}
\usepackage{amsmath}
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{authblk}
\textwidth=6.2in
\textheight=8.5in
%\parskip=.3cm
\oddsidemargin=.1in
\evensidemargin=.1in
\headheight=-.3in

\begin{document}
\SweaveOpts{concordance=TRUE}
\SweaveOpts{highlight=TRUE, tidy=TRUE, keep.space=TRUE, keep.blank.space=FALSE, keep.comment=TRUE}
\SweaveOpts{prefix.string=Fig}
%To put figures in subfolder
%\SweaveOpts{prefix.string=figures/fig}
\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=2em}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=2em}
\DefineVerbatimEnvironment{Scode}{Verbatim}{xleftmargin=2em}

\title{Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species}
\author[1]{\large Andrew T. Tredennick}
\author[1]{\large Peter B. Adler}
\author[2,3,4,5]{\large Mevin B. Hooten}
\author[5,6,7,8]{\large Cameron L. Aldridge}
\author[9]{\large Colin G. Homer}
\author[1]{\large David T. Iles}
\author[1]{\large Andrew Kleinhesselink}
\author[1]{\large Eric LaMalfa}
\author[1]{\large Rebecca Mann}
\affil[1]{\footnotesize \emph{Department of Wildland Resources and the Ecology Center, Utah State University}}
\affil[2]{\footnotesize \emph{U.S. Geological Survey, Colorado Cooperative Fish and Wildlife Research Unit}}
\affil[3]{\footnotesize \emph{Department of Fish, Wildlife, and Conservation Biology, Colorado State University}}
\affil[4]{\footnotesize \emph{Department of Statistics, Colorado State University}}
\affil[5]{\footnotesize \emph{Graduate Degree Program in Ecology, Colorado State University}}
\affil[6]{\footnotesize \emph{Department of Ecosystem Science and Sustainability, Colorado State University}}
\affil[7]{\footnotesize \emph{U.S. Geological Survey, Fort Collins Science Center}}
\affil[8]{\footnotesize \emph{Natural Resource Ecology Laboratory, Colorado State University}}
\affil[9]{\footnotesize \emph{U.S. Geological Survey (USGS) Earth Resources Observation and Science (EROS) Center}}
\maketitle

\section*{\large Summary}
\begin{enumerate}
\item Global environmental changes, like climate change, tend to play out at the landscape and regional scales. Thus, it is reasonable that attempts to forecast the impacts of such change do so at similar spatial scales. For plant species, this has meant relying primarily on a single tool, species distribution models, that contain little information on population dynamics and states.

@@

\noindent{}\textbf{Keywords:} population model, forecasting, integral projection model, etc.

>>>>

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in

---

Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species
===========================================================================================

### Andrew T. Tredennick[^corrauth], Mevin B. Hooten, Cameron L. Aldridge, Colin G. Homer, David T. Iles, Andrew Kleinhesselink, Eric LaMalfa, Rebecca Mann, and Peter B. Adler

*Andrew T. Tredennick, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, UT*

*Mevin B. Hooten, U.S. Geological Survey, Colorado Cooperative Fish and Wildlife Research Unit; Department of Fish, Wildlife, and Conservation Biology, Colorado State University; Department of Statistics, Colorado State University; Graduate Degree Program in Ecology, Colorado State University, Fort Collins, CO*

*Cameron L. Aldridge, Department of Ecosystem Science and Sustainability, Colorado State University; Natural Resource Ecology Laboratory, Colorado State University; U.S. Geological Survey, Fort Collins Science Center; Graduate Degree Program in Ecology, Colorado State University, Fort Collins, CO*

*Colin G. Homer, U.S. Geological Survey (USGS) Earth Resources Observation and Science (EROS) Center, Sioux Falls, SD*

*David T. Iles, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, UT*

*Andrew Kleinhesselink, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, UT*

*Eric LaMalfa, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, UT*

*Rebecca Mann, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, UT*

*Peter B. Adler, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, UT*

[^corrauth]: Corresponding author: [atredenn@gmail.com](mailto:atredenn@gmail.com)

Summary
-------
\begin{enumerate}
\item Global environmental changes, like climate change, tend to play out at the landscape and regional scales. Thus, it is reasonable that attempts to forecast the impacts of such change do so at similar spatial scales. For plant species, this has meant relying primarily on a single tool, species distribution models, that contain little information on population dynamics and states.

@@

*Keywords*: population model, forecasting, integral projection model, etc.
